Results_paper1

### 2019-04-16 Paper1_results.Rmd
Marked off the changes I made with RWS

load("Data_P1/site_list_sub.RData") # Loading the SACTN_overlap dataset which allows me to match it to the OISST data

@@

PN_wave <- dlply(PN_prewhite, .(site), wl.fun)

for (i in 1:length(PN_wave)) {
  attributes(PN_wave[[i]]) <- c(attributes(PN_wave[[i]]), ref = names(PN_wave)[i])
}
# x <- PN_wave[[3]]
plot_fun <- function(x, plot_name = attributes(x)$ref) {
  png(filename = paste0("Figures",plot_name,"_wavelets.png"),
      width = 800, height = 600, units = "px", pointsize = 12, bg = "white")
  wt.image(x, siglvl = 0.05, col.contour = "black", color.key = "quantile",
           timelab = "Days", verbose = FALSE, useRaster = TRUE,
           periodlab = "Period", lwd = 1, graphics.reset = FALSE,
           main = plot_name)
  dev.off()
}
ldply(PN_wave, plot_fun) 
```

@@

transect.pixel.isobath <- function(site, distance = 25000, isobath = 999){ # Only at a distance of 25000km
  # Extract coordinates
  coords <- data.frame(lon = site$lon, lat = site$lat)
  # Find lon/ lats every X metres 
  pixels <- data.frame()
  deep <- 999
  while(deep > isobath){
    # Find depth at distance step
    coords2 <- as.data.frame(destPoint(p = coords, b = site$heading, d = distance))
    sitesIdx <- knnx.index(sa_bathy[,1:2], as.matrix(coords2), k = 1)
    bathy2 <- sa_bathy[sitesIdx,]
    bathy2 <- bathy2[complete.cases(bathy2$depth),]
    bathy3 <- data.frame(site = site$site, lon = bathy2$lon, lat = bathy2$lat, 
                         heading = site$heading, depth = bathy2$depth)
    pixels <- rbind(pixels, bathy3)
    coords <- coords2
    deep <- bathy2$depth
  }
  pixels2 <- pixels[pixels$depth > -999,] 
  if(nrow(pixels2) < 1){
    pixels2 <- data.frame(site, depth = NA)
  }else{
    pixels2 <- pixels2
  }
  return(pixels2)
}

# Pixel points
site_pixels <- data.frame()
for(i in 1:length(west$site)){
  site <- site_transects[i,]
  site_pixel <- transect.pixel.isobath(site, 25000, -900)
  site_pixels <- rbind(site_pixels, site_pixel)
}

save(site_pixels, file = "Data_P1/site_pixels.RData")
load("Data_P1/site_pixels.RData")

@@

```{r}
wind_1 <- read.delim("Data_P1/Wind_data/wind_data.txt(SAWS)/wind1/wind1.txt", na.strings="") 
colnames(wind_1) <- c("station_number", "station_name", "date", "hour", "sub", "speed", "dir")

wind_2 <- read.delim("Data_P1/Wind_data/wind_data.txt(SAWS)/wind2/wind2.txt", na.strings="")
colnames(wind_2) <- c("station_number", "station_name", "date", "hour", "sub" ,"speed", "dir")

wind_3 <- read.delim("Data_P1/Wind_data/wind_data.txt(SAWS)/wind3/wind3.txt", na.strings="")
colnames(wind_3) <- c("station_number", "station_name", "date", "hour", "sub" ,"speed", "dir")

# Slecting the important columns for each of the datasets
wind_fix <- function(df){
wind <- df%>% 
  select(station_name, date, hour, dir, speed) #column names
}
wind_1 <- wind_fix(df = wind_1)
wind_2 <- wind_fix(df = wind_2)
wind_3 <- wind_fix(df = wind_3)

@@

renaming_sites_1 <- function(df) {
  sites <- df %>%
    mutate(temp_sites = ifelse(station_name %in% c("CAPE COLUMBINE"), "St Helena Bay",        
                           ifelse(station_name %in% c("KOINGNAAS"), "Hondeklipbaai",
                                ifelse(station_name %in% c("PORT NOLLOTH"), "Port Nolloth",
                                       ifelse(station_name %in% c("LAMBERTSBAAI NORTIER"), "Lamberts Bay",
                                              ifelse(station_name %in% c("LANGEBAANWEG AWS"), "Saldanha Bay
","Error"))))))
  return(sites)
}

wind_sitesmatched_1 <-  renaming_sites_1(df = wind_1)
wind_sitesmatched_1 <- wind_sitesmatched_1[-c(121352, 121353, 379892, 379893, 609324, 609325, 843506, 843507, 1014585), ]

@@

wind_data <- wind_data %>% 
  group_by(date,hour,temp_sites) %>% 
  mutate(date = as.Date(date))

@@

# LOading the wind data
library(tidyverse)
library(circular)
wind_data <- read_csv("wind_data.csv", col_types = cols(X1 = col_number(), date = col_character(), dir = col_number(), hour = col_number(),  speed = col_number()))

wind_daily <- wind_data %>% 
  mutate(date = as.Date(date))%>%
   group_by(temp_sites, date) %>%
   summarise(dir_circ = round(mean.circular(circular(dir, units = "degrees")),2),
             mean_speed = round(mean(speed),2))

@@

wind_daily_sub <- wind_daily %>% 
  dplyr::rename(site = temp_sites) %>% 
  filter(site %in% selected_sites) # ***Does not detect Saldanha Bay???****

@@

p.wr2 <- plot.windrose(data = wave_daily_renamed,
              spd = "spd",
              dir = "dir")
p.wr3 <- p.wr2 + facet_wrap(.~ site, ncol = 2, nrow = "") +
  theme(strip.text.x = element_text(size = 25))
p.wr3
```

@@

region <- "BC" # Benguela Current
coords <- bbox[, region]
coords <- c(-35, -20, 10, 20) # this is the BC

@@

daily_chloro_data <- chloro_data %>%
  dplyr::mutate(date = as.Date(date)) %>%
  dplyr::group_by(combi, lon, lat, date) %>%
  dplyr::summarise(chloro = mean(chloro, na.rm = TRUE)) %>%
  dplyr::group_by(combi, lon, lat, date) %>%
  tidyr::nest() %>%
  dplyr::mutate(clims = purrr::map(data, ts2clm, x = date, y = chloro,
                     climatologyPeriod = c("2002-07-13", "2018-12-04"),
                     maxPadLength = 8)) %>% # Adjust maxPadLength = X for longer interpolation
  dplyr::select(-data) %>%
  tidyr::unnest() %>%
  select(-doy, -seas, -thresh)
```

>>>>

load("Data_P1/site_list_sub.Rdata") # Loading the SACTN_overlap dataset which allows me to match it to the OISST data

@@

PN_wave <- dlply(PN_prewhite, .(site), wl.fun, .parallel = T) # RWS: Allow parallel processing

for (i in 1:length(PN_wave)) {
  attributes(PN_wave[[i]]) <- c(attributes(PN_wave[[i]]), ref = names(PN_wave)[i])
}
# x <- PN_wave[[3]]
plot_fun <- function(x, plot_name = attributes(x)$ref) {
  png(filename = paste0("Figures",plot_name,"_wavelets.png"),
      width = 800, height = 600, units = "px", pointsize = 12, bg = "white")
  wt.image(x, siglvl = 0.05, col.contour = "black", color.key = "quantile",
           timelab = "Days", verbose = FALSE, useRaster = TRUE,
           periodlab = "Period", lwd = 1, graphics.reset = FALSE,
           main = plot_name)
  dev.off()
}
ldply(PN_wave, plot_fun, .parallel = T) # RWS: Allow parallel processing
```

@@

transect.pixel <- function(site, distances){
  # Extract coordinates
  coords <- data.frame(lon = site$lon, lat = site$lat)
  # Find lon/ lats every X metres 
  pixels <- data.frame()
  # deep <- 999
  # distance_multiplier <- 1
  # while(deep > isobath){
  for(i in 1:length(distances)){
    # Add index to show distance from coast
    # Find depth at distance step
    coords2 <- as.data.frame(destPoint(p = coords, b = site$heading, d = distances[i]))
    sitesIdx <- knnx.index(sa_bathy[,1:2], as.matrix(coords2), k = 1)
    bathy2 <- sa_bathy[sitesIdx,]
    bathy2 <- bathy2[complete.cases(bathy2$depth),]
    bathy3 <- data.frame(site = site$site, lon = bathy2$lon, lat = bathy2$lat, 
                         heading = site$heading, 
                         # depth = bathy2$depth,
                         distance = distances[i])
    pixels <- rbind(pixels, bathy3)
    coords <- coords2
    # distance_multiplier <- distance_multiplier +1 
    # deep <- bathy2$depth
  }
  # pixels2 <- pixels[pixels$depth > -999,] 
  if(nrow(pixels) < 1){
    pixels <- data.frame(site, depth = NA)
  }else{
    pixels <- pixels
  }
  return(pixels)
}

# Pixel points
site_pixels <- data.frame()
for(i in 1:length(west$site)){
  site <- site_transects[i,]
  site_pixel <- transect.pixel(site, c(15000, 25000, 35000, 45000, 55000)) # RWS: The desired distances
  site_pixels <- rbind(site_pixels, site_pixel)
}

# save(site_pixels, file = "Data_P1/site_pixels.RData")
load("Data_P1/site_pixels.RData")

@@

```{r}
wind_1 <- read.delim("Data_P1/Wind_data/wind_data.txt(SAWS)/wind1/wind1.txt", na.strings = "", 
                     col.names = c("station_number", "station_name", "date", "hour", "sub", "speed", "dir"))

wind_2 <- read.delim("Data_P1/Wind_data/wind_data.txt(SAWS)/wind2/wind2.txt", na.strings = "",
                     col.names = c("station_number", "station_name", "date", "hour", "sub" ,"speed", "dir"))

wind_3 <- read.delim("Data_P1/Wind_data/wind_data.txt(SAWS)/wind3/wind3.txt", na.strings = "",
                     col.names = c("station_number", "station_name", "date", "hour", "sub" ,"speed", "dir"))

# Slecting the important columns for each of the datasets
wind_fix <- function(df){
wind <- df %>% 
  select(station_name, date, hour, dir, speed) %>%  #column names
  mutate(date = as.Date(as.character(date)),
         hour = as.numeric(as.character(hour)), 
         dir = as.numeric(as.character(dir)),
         speed = as.numeric(as.character(speed)))
}
# RWS: We can see when we force the values to be numeric that there are some non-numeric values in the base data
wind_1 <- wind_fix(df = wind_1)
wind_2 <- wind_fix(df = wind_2)
wind_3 <- wind_fix(df = wind_3)

@@

renaming_sites_1 <- function(df) {
  sites <- df %>%
      # RWS: An alternative way to replace values without having to use multiple ifelse() statements
      mutate(temp_sites = case_when(station_name == "CAPE COLUMBINE" ~ "St Helena Bay",
                                    station_name  == "KOINGNAAS" ~ "Hondeklipbaai",
                                    station_name  == "PORT NOLLOTH" ~"Port Nolloth",
                                    station_name  == "LAMBERTSBAAI NORTIER" ~ "Lamberts Bay",
                                    station_name  == "LANGEBAANWEG AWS" ~ "Saldanha Bay"))
  return(sites)
}

wind_sitesmatched_1 <-  renaming_sites_1(df = wind_1)
# RWS: You should never be removing values by specific call like this
  # Rather you should be able to use some sort of conditional to screen out unwanted values
wind_sitesmatched_1 <- wind_sitesmatched_1[-c(121352, 121353, 379892, 379893, 609324, 609325, 843506, 843507, 1014585), ]

@@

wind_data <- wind_data %>% 
  # mutate(date = as.Date(date)) %>%  
  group_by(date, hour, temp_sites)

@@

# Loading the wind data
library(tidyverse)
library(circular)

# wind_data <- read_csv("wind_data.csv", col_types = cols(X1 = col_number(), date = col_character(), dir = col_number(), hour = col_number(),  speed = col_number())) # Dataset too large for Github but better data at line 638

# wind_data <- read_csv("Data_P1/wind_data.csv")

wind_daily <- wind_data %>%
  # ungroup() %>%
  # mutate(date = as.Date(date))%>%
  dplyr::group_by(temp_sites, date) %>%
  dplyr::summarise(dir_circ = round(mean.circular(circular(dir, units = "degrees")),2),
                   mean_speed = round(mean(speed),2))

@@

wind_daily_sub <- wind_daily %>% 
  dplyr::rename(site = temp_sites) %>% 
  filter(site %in% selected_sites)

@@

p.wr2 <- plot.windrose(data = wave_daily_renamed,
              spd = "spd",
              dir = "dir")
p.wr3 <- p.wr2 + facet_wrap(.~ site, ncol = 2, nrow = "") +
  theme(strip.text.x = element_text(size = 25))
p.wr3 # RWS: You'll want to remove the NA part in the figure output
```

@@

region <- "BC" # Benguela Current
# coords <- bbox[, region] # RWS: Where does bbox come from?
coords <- c(-35, -20, 10, 20) # this is the BC

@@

daily_chloro_data <- chloro_data %>%
  # dplyr::mutate(date = as.Date(date)) %>% # RWS: The values already are dates
  dplyr::group_by(combi, lon, lat, date) %>%
  dplyr::summarise(chloro = mean(chloro, na.rm = TRUE)) %>%
  dplyr::group_by(combi, lon, lat) %>% # RWS: Deleted the date grouping variable being used here
  tidyr::nest() %>%
  dplyr::mutate(clims = purrr::map(data, ts2clm, x = date, y = chloro,
                     climatologyPeriod = c("2010-02-11", "2014-12-20"),
                     maxPadLength = 8)) %>% # Adjust maxPadLength = X for longer interpolation
  dplyr::select(-data) %>%
  tidyr::unnest() %>%
  select(-doy, -seas, -thresh)
```
